%{A small problem can lead to complicated and often unfathomable notions and solutions, which is the wonder of mathematics. The Brachistochrone curve, which began as a simple task to infer the shortest path between two objects in space aided by gravity, evolved into the Calculus of Variations, an entire field of mathematics.}

%{The very fact that this simple-sounding problem was the eventual reason for significant further advancement in the fields of mathematics and physics drew me to explore this problem and study it thoroughly.}

%{I discovered and read various Mathematical Association of America research papers through my ”basic” investigation, which I found while surfing Wikipedia late one night, Articles, lecture notes, books, physics applications.}

%{In the beginning, it was pretty complicated to understand the mathematics behind the analytical solutions placed by Euler and Lagrange. Still, after learning more about certain topics, I finally learned and understood them.}

%{This exploration enabled me to study the most basic yet important parts of the Calculus of Variations, a field foreign to me.}

%{Cetain topics used in this investigation are generally taught at an undergraduate level, but with time, I learnt and understood them with the use of mathematical intuition and rigour. Topics such as partial derivatives and functionals.}

%{This exploration enabled me to explore more mathematics on my own, and explore and fix my shortcomings and conceptual errors in my errors on mathematical understanding and ideas.}

{A small problem can lead to complicated and often unfathomable notions and solutions, which is the wonder of mathematics. The Brachistochrone curve, which began as a simple task to infer the shortest path between two objects in space aided by gravity, evolved into the Calculus of Variations, an entire field of mathematics. The very fact that this simple-sounding problem was the eventual reason for significant further advancement in the fields of mathematics and physics drew me to explore this problem and study it thoroughly.} 

{I discovered and read various Mathematical Association of America research papers through my ”basic” investigation, which I found while surfing Wikipedia late one night, Articles, lecture notes, books, physics applications. In the beginning, it was pretty complicated to understand the mathematics behind the analytical solutions placed by Euler and Lagrange. Still, after learning more about certain topics, I finally learned and understood them. This exploration enabled me to study the most basic yet important parts of the Calculus of Variations, a field foreign to me. Cetain topics used in this investigation are generally taught at an undergraduate level, but with time, I learnt and understood them with the use of mathematical intuition and rigour. Topics such as partial derivatives and functionals.} 

{This exploration enabled me to explore more mathematics on my own, and explore and fix my shortcomings and conceptual errors in my errors on mathematical understanding and ideas through a various means, for example this exploration has strengthened my analytical methods whereas it has also exposed me to a list of numerical methods, which could be evident by me using a Python script to prove my result's validity and back my findings.}

